---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rFTX

<!-- badges: start -->
<!-- badges: end -->

The goal of rFTX is to provide R interface for FTX REST API. The user is required to have an FTX account as the account’s API key and secret key is used in authentication. These can be created here: https://ftx.com/profile. If you are using a subaccount, some functions allow the name as an argument. This can be left out if not using subaccounts.

## Installation

rFTX package is not yet on CRAN but it will soon be.

You can install the development version from [GitHub](https://github.com/) with:

``` r
devtools::install_github("andreskull/rFTX", build_vignettes = TRUE)
```
## GET Example

This is a basic example which shows you how to fetch trades data for a particular market:

```{r example, message=FALSE}
library(rFTX)

## basic example code
ftx_trades(key = "", secret = "", market = "FTM-PERP")

```

This is another example which shows you how to fetch future funding rates data for two markets:

```{r example2, message=FALSE}
## second example code
ftx_future_funding_rates(key = "", secret = "", markets = c('CRV-PERP','XRP-PERP'))

```
